Topological Approach to Finding Blackholes in Directed Networks

### 2019-12-08 blackholes/pavt/article.tex
Smalll remarks and explanations.

The main contributor to the blackhole detecting problem is the authors from the University of New Jersey. They both formulated the task and proposed an algorithm for blackhole detection in case of unweighted directed graph \cite{li2010detecting}. 
Two years later they published an algorithm for approximate blackhole search in general case (weighted graph) \cite{li2012mining,li2014mining}. 
Hong et al \cite{hong2015detecting} consider application for online blackhole mining in the city environment. They introduced an original algorithm an approximate solution of the problem for dynamic graphs.

@@

\subsection{Problem Statement} 
First, consider a directed graph $G = G(V,E)$, where $V$ is a set of nodes and $E$ is a set if edges of the graph.

@@

\section{Topological Algorithm Design}
We propose to look at the blackhole search problem from the following: it would be divided into two independent tasks. 
The first one is graph preprocessing. Here we aim to simplify graph structure as far as it is possible with respect to a restricted time span. 
Decreased graph scale would definitely speed up the the calculation, as it can fall into a brute-force search in most cases.
The second is the blackhole search itself. This step is done after preprocessing and the goal here is to find as many blackholes as possible in a restricted time.

@@

Algorithm \ref{alg:isbasis} IsBasis tests a set of nodes as a blackhole basis. 
First, we need to know what special nodes there are. This step can be precalculated. 
\FIXME{как вычисляются global roots?}
To find out, we take every global root of the condensated graph and find topological sort of its closure.
Those vertices, which satisfy definition, we mark as special for according roots.

\FIXME{зачем второй этап?}
%\FIXME{partially implemented: по факту тут алгоритм применяется только к первому корню. Это было проще реализовать. }

@@

Third, when we are out of cheap heuristic, we check if any of the candidate nodes are reachable from one another. If so, we omit this set in the high-level TopSort (Algorithm \ref{alg:topsort}).

@@

The TopSort algorithm is based on looking over blackhole basises. Thus we have a valid basis of a blackhole.
To acquire blackhole we should, according to definition of basis, unite all the closures of basic nodes.
Finally, we check for weak connectivity and if it is present, then print the blackhole.

>>>>

The main contributor to the blackhole detecting problem is the authors from the University of New Jersey. They both formulated the task and proposed an algorithm for blackhole detection in case of unweighted directed graph \cite{li2010detecting}. 
Two years later they published an algorithm for approximate blackhole search in general case (weighted graph) \cite{li2012mining,li2014mining}. 
Hong et al \cite{hong2015detecting} consider application for online blackhole mining in the city environment. They introduced an original algorithm approximately solving the problem for dynamic graphs.

@@

\subsection{Problem Statement} 
First, consider a directed graph $G = G(V,E)$, where $V$ is a set of nodes and $E$ is a set of edges of the graph.

@@

\section{Topological Algorithm Design}
We propose to look at the blackhole search problem from the following: it would be divided into two independent tasks. 
The first one is graph preprocessing. Here we aim to simplify graph structure as far as it is possible with respect to a restricted time span. 
Decreased graph scale would definitely speed up the calculation, as it can fall into a brute-force search in most cases.
The second is the blackhole search itself. This step is done after preprocessing and the goal here is to find as many blackholes as possible in a restricted time.

@@

Algorithm \ref{alg:isbasis} IsBasis tests a set of nodes as a blackhole basis.
This algorthm takes a set of nodes as input. It returns $True$, if given set forms a proper basis,
and  $False$ otherwise. This algortihm is used as a part of TopSort \ref{alg:topsort} algorithm, which is looking over
blackhole basis candidates and sorts unproper ones out. If $IsBasis$ returns False on a basis candidate, this candidate is to be omitted.

IsBasis algorithm does the following.
First, we need to know what special nodes there are. This step can be precalculated. 
\FIXME{как вычисляются global roots?}
\begin{remark}
    Those nodes of graph G(V,E) that have no incoming edges are called $Global\ roots$. 
\end{remark}
To find out, we take every global root of the condensated graph and find topological sort of its closure.
Those vertices, which satisfy definition, we mark as special for according roots.

\FIXME{зачем второй этап?}
\FIXME{Ответ: тут случаи отсеиваются за счет эвристики. Это дешево.}
%\FIXME{partially implemented: по факту тут алгоритм применяется только к первому корню. Это было проще реализовать. }

@@

Third, when we are out of cheap heuristics, we check if any of the candidate nodes are reachable from one another. 
If so, we omit this set.

@@

If all previous checks did not return $False$ (omit), then $IsBasis$ returns $True$.
Thus we return to TopSort algorithm and we have a valid basis of a blackhole.
To acquire blackhole we should, according to definition of basis, unite all the closures of basic nodes.
Finally, we check for weak connectivity and if it is present, then print the blackhole.
